A Simplified Plackett-Luce Likelihood Function for Rank Orders

### 2025-01-20 inst/hankin-AustrianJournalofStatistics.tex
cite R as specified in the AJS style guide

\noindent where $B=1/b$.  Note carefully that these expressions are
likelihoods, not probabilities, and do not sum to 1.  Previous related
work \citep{hankin2024_hyper3} presented the case $n=3$ [in current
  notation] but here arbitrary $n$ may be considered.  Taking the case
$n=9$, for example, gives us 9 distinct likelihood functions,
Figure~\ref{ninelikes}.  We see an unanticipated asymmetry between $r$
and $n-r$.  For $r=5$ one might expect that $\hat{a}=\frac{1}{2}$ on
the grounds that the focal competitor's performance was median.
However, $\hat{a}\simeq 0.5886$.  Figure~\ref{dotprobs} shows the
maximum likelihood estimator $\hat{a}$ for various values of $n,r$,
obtained by direct numerical maximization of
equation~\ref{likeforrn3}.

>>>>

\noindent where $B=1/b$.  Note carefully that these expressions are
likelihoods, not probabilities, and do not sum to 1.  Previous related
work \citep{hankin2024_hyper3} presented the case $n=3$ [in current
  notation] but here arbitrary $n$ may be considered.  Taking the case
$n=9$, for example, gives us 9 distinct likelihood functions,
Figure~\ref{ninelikes}.  We see an unanticipated asymmetry between $r$
and $n-r$.  For $r=5$ one might expect that $\hat{a}=\frac{1}{2}$ on
the grounds that the focal competitor's performance was median.
However, $\hat{a}\simeq 0.5886$.  Figure~\ref{dotprobs} shows the
maximum likelihood estimator $\hat{a}$ for various values of $n,r$,
obtained by direct numerical maximization, in the R programming
language \cite{rcore2024}, of equation~\ref{likeforrn3}.
